---
title: "T15-03 Presentation"
author: "Yifan Jin, Stuart Morrison, Derek Ng, Christopher Saad"
date: "31/10/2019"
output:
  html_document: default
  revealjs::revealjs_presentation:
    fig_height: 12
    fig_width: 15
    theme: solarized
---

## Introduction
<script src="http://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=12, fig.height=4) 
```

```{r, include=FALSE}
library(tidyverse)
library(wesanderson)
# devtools::install_github("karthik/wesanderson")
library(scales)
library(stringr)
library(grid)
library(gridExtra)
library(caret)
library(broom)
library(kableExtra)
```

- Dataset representing prenatal risk factors and child birth weight
- We examine how certain risk factors mothers show while pregnant effect the infant's birth weight with a multiple lienar regression model
- We find that each of the risk factors we examine has a statistically significant effect on a infant's birth weight - ie, putting the infant at risk

## The data we use in our analysis

- Our data was originally collected by physicians in 1986 to examine the effects of risk factors on the birth weight of an infant (Hosmer, David W., et al., 2013) - included in the `MASS` package
- Low birth weight is associated with higher infant morality rates and birth defect rates
- It contains observations on 189 different pregnancies
 

## Having a look at the data

- There are 10 variables included in the data
- The key dependent variable for this analysis is:
  + `birthwt` - a variable measuring the infant's weight at birth
- The risk factors we examine are:
  + the racial background of the mother
  + whether the mother is a smoker
  + whether the mother has had a premature labour before
  + whether the mother experiences hypertension
  + whether the mother experiences physical irritability

```{r message=FALSE,error=FALSE,echo=FALSE}
library(MASS)
ourdata <- birthwt %>% 
            mutate(
                    # Reduce number of premature labours to true or false.
                    race = factor(race, labels = c("White", "Black", "Other")), # Organise race
                    smoke = factor(smoke, labels = c("False", "True")), # Organise smokes
                    ftv = factor(ftv)
                   )
levels(ourdata$ftv)[-(1:2)] <- "2+" # Organises physicisian visits to, 0, 1 or 2+.
colnames(ourdata) <- c("below_2500", "age",
                      "mother_weight", "race",
                      "smokes", "previous_prem_labor",
                      "hypertension", "uterine_irr",
                      "physician_visits", "birth_weight")
ourdata <- dplyr::select(ourdata, -c(below_2500))
```

## The distribution of birth weights

- `r (sum(ourdata$birth_weight < 2500) / nrow(ourdata)) %>% percent()` of the infants in our data had a clinically low birth weight

```{r message=FALSE,error=FALSE,echo=FALSE}
ggplot()+
  # Plot histogram of birth weights
  geom_histogram(data = ourdata,
                 aes(x = birth_weight),
                 fill = wes_palettes$Zissou1[1]) +
  # Put a vertical line at what is considered low birth weight, ie, 2500 grams
  geom_vline(xintercept = 2500,
             linetype = 2, size = 1.2,
             col = wes_palettes$Zissou1[3]) +
  # Make labels, etc pretty
  theme_bw(base_size = 18) +
  labs(x = "Birth weight (grams)",
       y = "Frequency") +
  scale_x_continuous(labels = comma) +
  theme(panel.background = element_rect(fill = "transparent"))
  
```

## The demographics represented in our data

```{r message=FALSE,error=FALSE,echo=FALSE}
# Plot a frequency plot of age
g_age <- ggplot() +
  facet_wrap(~ variable) +
  geom_bar(data = ourdata %>%
                    dplyr::select(age) %>%
                    gather(variable, value) %>%
                    mutate(variable = stringr::str_to_title(variable)),
           aes(x = value), fill = wes_palettes$Darjeeling1[2],
           stat = "count") +
  # Plot a bar at the median age
  geom_vline(xintercept = median(ourdata$age),
             linetype = 2, size = 1.2,
             col = wes_palettes$Darjeeling1[1]) +
  labs(x = "", y = "Frequency") +
  theme_bw(base_size = 18) +
  theme(panel.background = element_rect(fill = "transparent"))
# Plot a frequency plot of smoking
g_smoke <- ggplot() +
  facet_wrap(~ variable) +
  geom_bar(data = ourdata %>%
                    dplyr::select(smokes) %>% 
                    gather(variable, value) %>% 
                    mutate(variable = stringr::str_to_title(variable)),
           aes(x = value), fill = wes_palettes$Darjeeling1[3],
           stat = "count") +
  labs(x = "", y = "") +
  theme_bw(base_size = 18) +
  theme(panel.background = element_rect(fill = "transparent"))
# Plot a frequency plot of race
g_race <- ggplot() +
  facet_wrap(~ variable) +
  geom_bar(data = ourdata %>%
                    dplyr::select(race) %>% 
                    gather(variable, value) %>% 
                    mutate(variable = stringr::str_to_title(variable)),
           aes(x = value), fill = wes_palettes$Darjeeling1[4],
           stat = "count") +
  labs(x = "", y = "") +
  theme_bw(base_size = 18) +
  theme(panel.background = element_rect(fill = "transparent"))
# Plot each of the plots together
gridExtra::arrangeGrob(g_age, g_smoke, g_race, nrow = 1) %>% 
  plot()
```

## Data cleaning and verascity 

- No variables appear to have erroneous measurements - birth weights and ages are in in the expected range
- We convert categorical variables to factors
- Drop extraneous variables from the data, such as the indicator function `low` that shows whether the infant had a low birthweight

## Model selection

- AIC is an indicator of quality of model - the less AIC the better quality we get

- Three approaches: 
  + `Backward selection with AIC` - drop variables in full model to get model which has lower AIC
  + `Forward selection with AIC` - add variables in null model to get model which has lower AIC
  + `Backward selection with p-value` - drop the variable with largest p-value in orginal model

## Model selection (cont.)

- Result:

```{r message=FALSE,error=FALSE,echo=FALSE}
# Run the linear model with all variables
bwt_lm1 = lm(ourdata$birth_weight ~ ., data = ourdata)
# Find the model based on AIC
step_back_aic <- step(bwt_lm1, direction = "backward", trace = F)
# Print the summary of the model
broom::tidy(step_back_aic) %>% 
  kable(digits = 2) %>%
        kable_styling(bootstrap_options = c("striped", "hover"), 
                      full_width = TRUE)
```



## Assumptions checking
- The residuals $\varepsilon_i$ are $iid$ $N(0,\sigma^2)$ and there is a linear relationship between y and x.
  + Linearity
  + Independence
  + Homoskedasticity
  + Normality
  

## Linearity, Independence and Homoskedasticity
```{r,message=FALSE,error=FALSE,echo=FALSE,size="Large"}
library(ggfortify)
autoplot(step_back_aic, which = 1) +
  theme_bw(base_size = 18)
```

## Normality
```{r,message=FALSE,error=FALSE,echo=FALSE}
library(ggfortify)
autoplot(step_back_aic, which=2)+theme_bw(base_size = 18)
```



## Results - Interpretation of Coefficients

```{r,message=FALSE,error=FALSE,echo=FALSE}
broom::tidy(step_back_aic) %>% 
  kable(digits = 2) %>%
        kable_styling(bootstrap_options = c("striped", "hover"), 
                      full_width = TRUE)
```

## Results - In-sample Performance
- Full Model
```{r}
summary(bwt_lm1)$r.squared
```
- Simplified Model
```{r}
summary(step_back_aic)$r.squared
```
## Results - Out-of-sample Performance
- Full Model
```{r,message=FALSE,error=FALSE,echo=FALSE}
set.seed(2)
cv_full = train(data = ourdata, birth_weight ~., method = 'lm', trControl= trainControl(method='cv',number = 10, verboseIter = FALSE))
cv_full
```
## Results - Out-of-sample Performance
- Simplified Model
```{r,message=FALSE,error=FALSE,echo=FALSE}
cv_simplified = train(data = ourdata, birth_weight ~ mother_weight + race + smokes + hypertension + uterine_irr, method = 'lm', trControl= trainControl(method='cv',number = 10, verboseIter = FALSE))
cv_simplified
```

## Conclusion

- We examined how certain risk factors effect the infant's birth weight
- We applied a multiple linear regression model to delineate the effect of each of the factors
- We find that each of the risk factors we examine have a statistically significant effect on a infant's birth weight - ie, putting the infant at risk
- Potential limitation - data was recorded at a charity health centre so our data may not represent the population of mothers
